\subsection*{Abstract}
% Problem statement.
Onion services are anonymous TCP services that are exposed over the Tor network.
As of November 2017 more than 50,000 onion services make available web sites,
chat protocols, and file sharing services.  Compared to conventional Internet
services, onion services exhibit higher latency, can only be accessed over Tor,
are barely indexed by search engines, and employ long, self-authenticating
domain names.  Our understanding of how users deal with these peculiarities is
limited to anecdotal evidence.
% What we are doing.
In this work we fill this gap by studying how people perceive, understand, and
use onion services.  To that end we employ a mixed-methods approach consisting
of semi-structured interviews to explore the problem space, and an online survey
to solicit answers to concrete questions.  We find that \first users place great
trust in The Tor Project but distrust content that is hosted on onion services,
\second users have devised a diverse set of methods to work around the
non-memorable domain format, \third some users have flawed mental models of the
underlying technology, and \fourth users not only rely on onion services for
anonymity but also for their security and NAT-punching properties.
% Why our work matters.
Our work enables The Tor Project to focus its efforts on the most pressing
usability issues, and improve its documentation by addressing common
misconceptions that we identified.  Our findings on self-authenticating domain
names generalize to other systems such as the Bitcoin network.
